---
title: "Degradation"
author: "David Hemprich-Bennett"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
#bibliography: /users/davidbennett/Dropbox/Bibtex/library.bib
#bibliography: '~/Dropbox/Bibtex/My_Library.bib'

---
```{r setup, include=FALSE}
#setwd('~/Dropbox/Education/PhD/Bat-diet/')
library(knitr)
knitr::opts_chunk$set(echo = F)
```

#Abstract
 
#Introduction


#Causes of degradation
* A natural process, being accelerated in the anthropocene
* Define it. Acknowledge that there's bloody loads of definitions 
* Borneo-specific stuff 
* Habitat loss and degradation combined threaten 44.8 percent of species (WWF Living planet report
** (from bats in the anthropocene) A pan-tropical meta-analysis of land-use change studies points to the irreplaceable value of old-growth forests, but also highlights the high species diversity found in regenerating logged forests compared to secondary forests (Gibson et al. 2011)*

#Consequences of degradation
* Need to consider the habitat effects for both secondary consumers, primary consumers and primary producers
* Loss of roost sites
* Work on birds in Brazil's Atlantic rainforest (unpublished) showed that the loss of specialist insectivorous birds led to an increase in insect herbivores %(see note on Cristina Banks-Leite from the Ceesymposium)
* Matrix type as well as distance for fragmentation is important
* General trend towards functional homogenisation 
    * Lower diversity of bats captured at SAFE than other two sites (need to use iNEXT to show this)
    * Insect diversity literature for Borneo?
* What we know from the bats of the neotropics
* Bat diet %Cite Hernani's stuff
*We need to be careful when making comparisons, as Zhan and MacIsaac 2015 -  Rare biosphere exploration using high-throughput sequencing: research progress and perspectives - state, much variation is caused by the random encounter of rare sequences when sampling or in the lab. This can cause erroneous findings of beta diversity

*Protected areas generally have higher biodiversity than non-protected areas [@Gray2016]
#Methods

```{r otu_conclusion_check, echo=FALSE}
#library(knitr)
#setwd('~/Dropbox/Education/PhD/Bat-diet/')
read_chunk('scripts/r/otu_conclusion_check_output_use.R')
```

```{r get_output, echo=FALSE}
#library(knitr)
#setwd('~/Dropbox/Education/PhD/Bat-diet/')
<<setup>>
``` 
#Results

#Discussion