---
title: "Degradation"
author: "David Hemprich-Bennett"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
#bibliography: /users/davidbennett/Dropbox/Bibtex/library.bib
#bibliography: '~/Dropbox/Bibtex/My_Library.bib'

---

```{r echo=FALSE}
library(knitr)
```



```{r echo=FALSE, cache=FALSE}
read_chunk('scripts/r/sitewise_inext.R')
```

```{r echo=FALSE, cache=FALSE}
read_chunk('scripts/r/betalink_analysis.R')
```

```{r echo=FALSE, cache=FALSE}
read_chunk('scripts/r/sample_size.R')
```

```{r echo=FALSE, cache=FALSE}
read_chunk('scripts/r/species_removal.R')
```

#Abstract
 
#Introduction

Habitat loss and degradation are the most common threat to the persistence of terrestrial species (WWF, 2016), affecting large areas of palaeotropical forests. This is particularly true of Borneo, a biodiversity hotspot in the Malay Archipelago where 62% of remaining forest has been classified as being degraded (Bryan et al., 2013). Although primary forests have been shown to be ‘irreplacable’ in terms of biodiversity, logged forests are more biodiverse than secondary forest and so are worthy of conservation concern (Gibson et al., 2011). Despite the rate of global deforestation having reduced in the last 25 years (FAO Forestry, 2015), attention must be given to degraded forest due to the low priority given to their protection against agricultural expansion (Gibbs et al., 2010).

#Causes of degradation
* A natural process, being accelerated in the anthropocene
* Define it. Acknowledge that there's bloody loads of definitions 
* Borneo-specific stuff 
* Habitat loss and degradation combined threaten 44.8 percent of species (WWF Living planet report
* (from bats in the anthropocene) A pan-tropical meta-analysis of land-use change studies points to the irreplaceable value of old-growth forests, but also highlights the high species diversity found in regenerating logged forests compared to secondary forests (Gibson et al. 2011)*

#Consequences of degradation
* Need to consider the habitat effects for both secondary consumers, primary consumers and primary producers
* Loss of roost sites
* Work on birds in Brazil's Atlantic rainforest (unpublished) showed that the loss of specialist insectivorous birds led to an increase in insect herbivores %(see note on Cristina Banks-Leite from the Ceesymposium)
* Matrix type as well as distance for fragmentation is important
* General trend towards functional homogenisation 
    * Lower diversity of bats captured at SAFE than other two sites (need to use iNEXT to show this)
    * Insect diversity literature for Borneo?
* What we know from the bats of the neotropics
* Bat diet %Cite Hernani's stuff
*We need to be careful when making comparisons, as Zhan and MacIsaac 2015 -  Rare biosphere exploration using high-throughput sequencing: research progress and perspectives - state, much variation is caused by the random encounter of rare sequences when sampling or in the lab. This can cause erroneous findings of beta diversity

*Protected areas generally have higher biodiversity than non-protected areas [@Gray2016]

#Methods

```{r sample_count_setup, echo=FALSE, message=FALSE, warning=FALSE}

```


#Results

##Sample size effects
```{r inext_setup, echo=FALSE, message=FALSE}

```

in Figure \ref{fig:inext} we see the different rates of MOTU accumulation at each site.

```{r inext_plot, echo = FALSE, message=FALSE, fig.width=7,fig.height=6,fig.cap="\\label{fig:inext}interpolation and extrapolation of MOTU diversity at each site"}
```

```{r inext_dataframe, echo =FALSE, message=FALSE}

```

```{r species_removal, echo =FALSE, message=FALSE, fig.width=10,fig.height=10,fig.cap="\\label{fig:sp_removal}The importance of each bat species to their network"}

```



##Beta-diversity

```{r betalink_setup_and_plot, echo=FALSE, message=FALSE}

```


##Networks and reliability of MOTU


#Discussion